Covariate analysis of ROSMAP Reprocessed RNASeq (with SVA)

### 2016-07-13 code/Rmd/ROSMAP_RNASeq_SVA_Reprocessed.Rmd
Minor modifications

# Permute and calculate the permuted singular values
PERM.SING.VALS <- foreach (i = 1:100,
         .combine = rbind,
         .packages = c('limma','CovariateAnalysis'),
         .export = c('PROCESSED_COUNTS','MODEL1')) %dopar% {
  PERM.COUNTS <- t(apply(PROCESSED_COUNTS$filteredExprMatrix, 1, sample, replace = FALSE))
  # Estimate voom weights
  VOOM.ADJUSTED.PERM.GENE_EXPRESSION = voom(PERM.COUNTS, design=MODEL1, plot=F)

  # Fit linear model using new weights and new design
  VOOM.ADJUSTED.PERM.FIT = lmFit(VOOM.ADJUSTED.PERM.GENE_EXPRESSION)

  # Residuals after normalisation
  RESIDUAL.PERM.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.PERM.FIT,VOOM.ADJUSTED.PERM.GENE_EXPRESSION$E)

  PERM.SINGULAR.VAL.DECOM <- svd(RESIDUAL.PERM.GENE_EXPRESSION)
  PERM.SING.VALS <- PERM.SINGULAR.VAL.DECOM$d[1:NUM.DEG.FREEDOM]^2/sum(PERM.SINGULAR.VAL.DECOM$d[1:NUM.DEG.FREEDOM]^2)
}
num.sv1 = sum(SING.VALS > t(rowMeans(t(PERM.SING.VALS)))[1,1])

num.sv2 = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456)
NUM.SV = min(num.sv1, num.sv2)

@@

### Residual calculation
Calculate weighted residuals and add back "cogdx" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("cogdx", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```

### Clustering residual data
```{r decompse.normalise.data2, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION, scale.=T)

>>>>

# # Permute and calculate the permuted singular values
# PERM.SING.VALS <- foreach (i = 1:100,
#          .combine = rbind,
#          .packages = c('limma','CovariateAnalysis'),
#          .export = c('PROCESSED_COUNTS','MODEL1')) %dopar% {
#   PERM.COUNTS <- t(apply(PROCESSED_COUNTS$filteredExprMatrix, 1, sample, replace = FALSE))
#   # Estimate voom weights
#   VOOM.ADJUSTED.PERM.GENE_EXPRESSION = voom(PERM.COUNTS, design=MODEL1, plot=F)
#   
#   # Fit linear model using new weights and new design
#   VOOM.ADJUSTED.PERM.FIT = lmFit(VOOM.ADJUSTED.PERM.GENE_EXPRESSION)
#   
#   # Residuals after normalisation
#   RESIDUAL.PERM.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.PERM.FIT,VOOM.ADJUSTED.PERM.GENE_EXPRESSION$E)
#   
#   PERM.SINGULAR.VAL.DECOM <- svd(RESIDUAL.PERM.GENE_EXPRESSION)
#   PERM.SING.VALS <- PERM.SINGULAR.VAL.DECOM$d[1:NUM.DEG.FREEDOM]^2/sum(PERM.SINGULAR.VAL.DECOM$d[1:NUM.DEG.FREEDOM]^2)
# }
# num.sv1 = sum(SING.VALS > t(rowMeans(t(PERM.SING.VALS)))[1,1])

num.sv2 = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456)
NUM.SV = num.sv2 #min(num.sv1, num.sv2)

@@

### Residual calculation
Calculate weighted residuals and add back "cogdx" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("cogdx", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(VOOM.ADJUSTED.FIT$design[,varsToAddIn])
```

### Clustering residual data
```{r decompse.normalise.data2, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION, scale.=T, center = T)
